### 2023-01-18 draft.tex
Deploying to gh-pages from @ gottacatchenall/ms_false_negatives@d94f60669f977395219738fc8e002f2be9273b27 🚀

In this section, we demonstate how difference in relative-abundance can
lead to many false-negatives in interaction data. We also introduce a
method for producing a null estimate of the false-negative-rate in
datasets via simulation, and a method for incorporating uncertainty
directly into predictions of species interactions to account for
observation error.

@@

From fig.~\ref{fig:geometric}(A) it is clear that the more often we see
two species co-occurring, but \emph{not interacting}, the more likely
the interaction is a true-negative. This has several practical
consequences: first it means negatives taken outside the overlap of the
range of each species aren't informative because co-occurrence was not
possible, and therefore neither was an interaction. Second, we can use
this relation to compute the expected number of total observations
needed to obtain a ``goal'' number of observations of a particular pair
of species (fig.~\ref{fig:geometric}(B)). As an example, if we
hypothesize that \(A\) and \(B\) do not interact, and we want to see
species \(A\) and \(B\) both co-occurring and \emph{not interacting} 10
times to be confident this is a true negative, then we need an expected
1000 observations of all species if the relative abundances of \(A\) and
\(B\) are both \(0.1\).

Because the true FNR is latent, we can never actually be sure what the
actual number of false-negatives in our data---however, we can use
simulation to estimate the FNR for datasets of a given size using
neutral models of observation. If some of the ``worst-case'' FNRs
presented in fig.~\ref{fig:geometric}(A) seem unrealistically high,
considering that species are observed in proportion to their relative
abundance. In the next section we demonstrate that the distribution of
abundance in ecosystems can lead to very high realized values of FNR
(\(p_{fn}\)) simply as an artifact of sampling effort.

>>>>

In this section, we demonstate how differences in species'
relative-abundance can lead to many false-negatives in interaction data.
We also introduce a method for producing a null estimate of the
false-negative-rate in datasets via simulation. Because the true
false-negative-rate is latent, we can never actually be sure how many
false-negatives are in our data. However, here we outline an approach to
deal with this fact---first by using simulation to estimate the
false-negative-rate for a dataset of a fixed size using neutral models
of observation. We then illustrate how to incorporate uncertainty
directly into predictions of species interactions to account for
observation error based on null estimates of both false-positive rates
(as an priori estimate of species misidentification probability) and
false-positive rates (as generated via the method we introduce).

@@

From fig.~\ref{fig:geometric}(A) it is clear that the more often we see
two species co-occurring, but \emph{not interacting}, the more likely
the interaction is a true-negative. This has several practical
consequences: first it means negatives taken outside the overlap of the
range of each species aren't informative because co-occurrence was not
possible, and therefore neither was an interaction. If some of the
``worst-case'' FNRs presented in fig.~\ref{fig:geometric}(A) seem
unrealistically high, considering that species are observed in
proportion to their relative abundance. In the next section we
demonstrate that the distribution of abundance in ecosystems can lead to
very high realized values of FNR (\(p_{fn}\)) simply as an artifact of
sampling effort. Second, we can use this relation to compute the
expected number of total observations needed to obtain a ``goal'' number
of observations of a particular pair of species
(fig.~\ref{fig:geometric}(B)). As an example, if we hypothesize that
\(A\) and \(B\) do not interact, and we want to see species \(A\) and
\(B\) both co-occurring and \emph{not interacting} 10 times to be
confident this is a true negative, then we need an expected 1000
observations of all species if the relative abundances of \(A\) and
\(B\) are both \(0.1\).
